---
title: "Bayesian Statistics - The Fun Way! #Chapter 13"
author: "Philibertus88"
date: "2022-10-21"
output: 
  html_document:
    code_folding: show
    theme: yeti
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = TRUE, message = FALSE, error = TRUE)
```

# Chapter 13:

```{r packages}
require(tidyverse)
```

```{r figure1}
x <- seq(0.005,0.01,by = 0.00001)
y <- dbeta(x,300,39700)

tbl <- tibble("x" = x, "y" = y)
tbl %>%
  ggplot(aes(x = x, y = y, color = y)) +
  geom_point(size = 0.1) +
  theme_bw() +
  geom_vline(xintercept = 300/40000, linetype = "dashed", color = "grey60") +
  scale_color_viridis_c() +
  labs(x = "Probability of subscription", y = "Density", title = "PDF beta(300,39700)")
```


How much more likely is it that the true conversion rate is 0.001 higher/lower than the mean of 0.0075?
We can take the integral of the dbeta distribution from 0 up to 0.0065 / or from 0.0085 up to 1.
Eventhough we have limited data using cumulative density function (CDF)

```{r}
lower <- pbeta(0.0065, 300, 39700)
#[1] 0.007978686

higher <- pbeta(1,300,39700) - pbeta(0.0085, 300, 39700)
#[1] 0.01248151

higher/lower
#[1] 1.564357
```

The true conversion rate is about 1.5x more likely to be actually higher than the estimated mean 0f 0.0075
```{r figure2}
tbl %>%
  ggplot(aes(x = x, y = y)) +
  geom_point(size = 0.1) + 
  geom_ribbon(data = subset(tbl, x > 0 & x <0.0065), 
              aes(ymax = y), xmax = 0.0065, ymin = 0, xmin = 0,
              fill = "firebrick", 
              alpha = 0.5) +
  geom_ribbon(data = subset(tbl, x > 0.0085 & x < 1),
              aes(ymax = y), ymin = 0, xmax = 1, xmin = 0.0085,
              fill = "steelblue",
              alpha = 0.5) +
  theme_bw() +
  geom_vline(xintercept = 300/40000, linetype = "dashed", color = "grey60") +
  scale_color_viridis_c() +
  labs(x = "Probability of Subscription", y = "Density", title = "PDF beta(300,39700)")
```

```{r figure 3}

#calculate the median of the CDF:
tbl$CDF <- pbeta(tbl$x, 300, 39700)
median(tbl$CDF)
#or derived visually:

CDFplot <- tbl %>%
  ggplot(aes(x = x, y = CDF, color = CDF)) +
  geom_point(size = 0.1) +
  theme_bw() +
  labs(y = "Cumulative probability", x = "Probability of Subscription",
       title = "CDF for E-Mail Conversion", subtitle = "Horizontal lines indicate 95% Confidence Interval\n 95% CI: approx. 0.0067 - 0.0084 (dashed red lines)") +
  #geom_hline(yintercept = median(tbl$CDF), linetype = "dashed", color = "grey60") +
  geom_hline(yintercept = 0.025, linetype = 1, color = "grey60") +
  geom_hline(yintercept = 0.975, linetype = 1, color = "grey60") +
  geom_vline(xintercept = 0.0067, linetype = 2, color = "red") +
  geom_vline(xintercept = 0.0084, linetype = 2, color = "red")

#The quantile function does the reverse of the CDF, i.e. it starts with a probability
#(e.g. you want to know the 95% confidence interval for probability of subscription)
#and provides you with precise numbers rather than starting with plotting and then deducing the 95% confidence
#interval "visually":
true_0.025percentCI <- qbeta(0.025, 300, 39700)
true_0.975percentCI <- qbeta(0.975, 300, 39700)
CDFplot +
  geom_point(aes(y = 0.025, x = true_0.025percentCI), color = "gold", size = 6, shape = 3) +
  geom_point(aes(y = 0.975, x = true_0.975percentCI), color = "gold", size = 6, shape = 3) +
  labs(caption = "While still very close, the quantile function qbeta(0.025, 300, 39700) and\n
       qbeta(0.975, 300, 39700) provide us the actual values (yellow cross)")
```



Exercises
**1 Plot Quantile Function:**
```{r figure5}
xs <- seq(0.001,0.99,by = 0.001)
quantile <- qbeta(xs, 300, 39700)
tbl2 <- tibble("Quantile" = xs, "Probability of Subscription" = quantile)
tbl2 %>%
  ggplot(aes(x = Quantile, y = `Probability of Subscription`)) +
  geom_point(size = 0.1) +
  theme_bw()
```

**2 What's the 99.9% Confidence Interval of snow fall?**
```{r}
snowfall <- c(7.8, 9.4, 10, 7.9, 9.4, 7.0, 7.0, 7.1, 8.9, 7.4)
length(snowfall) #10

mean_snow <- mean(snowfall)
sd_snow <- sd(snowfall)

qnorm(0.0005, mean = mean_snow, sd = sd_snow) #4.456
qnorm(0.9995, mean = mean_snow, sd = sd_snow) #11.924
```

The 99.9% Confidence Interval lies between 4.456 and 11.924 inches of snow.


**3 How many candy bars will likely be sold with the next 40 house visits?**
```{r}
#30 houses
#10 candy bars
#alpha = 10, beta = 20

lowerBound <- qbeta(0.025, 10,20)
upperBound <- qbeta(0.975, 10,20)

lowerBound * 40 #7.175346
upperBound * 40 #20.33293
```
We're pretty certain that she will sell *between 7 and 20* candy bars.
